Clique and Constraint Models for Maximum Common (Connected) Subgraph Problems

### 2016-09-02 talk/talk.tex
Split this in two

\begin{frame}{Connectedness as a Constraint}
    \begin{itemize}
        \item Once we have assigned one variable to a non-$\bot$ value, traverse the variable graph,
            ignoring any variables assigned to $\bot$. Assign any unvisited variables to $\bot$.
        \item Repeat whenever any variable is assigned to $\bot$ during search.
        \item Also, traverse the value graph, ignoring any values not present in any domain. Remove
            any unvisited values from every domain.
        \item Repeat whenever a value is removed from every domain during search.
    \end{itemize}
\end{frame}

@@

\begin{frame}{Connectedness in Clique-Like Algorithms}
    \begin{itemize}
        \item Connectedness doesn't decompose cleanly into binary constraints, so we can't encode it
            as microstructure.
        \item On the other hand, we \emph{can} use restricted branching, if we give more information
            to the clique algorithm.
            \begin{itemize}
                \item Integrating this with the bound and ordering heuristic is horribly technical.
            \end{itemize}
    \end{itemize}
\end{frame}

>>>>

\begin{frame}{Connectedness as a Constraint (on Variables)}
    \begin{itemize}
        \item Once we have assigned one variable to a non-$\bot$ value, traverse the variable graph,
            ignoring any variables assigned to $\bot$. Assign any unvisited variables to $\bot$.
        \item Repeat whenever any variable is assigned to $\bot$ during search.
    \end{itemize}
\end{frame}

\begin{frame}{Connectedness as a Constraint (on Values)}
    \begin{itemize}
        \item Also, traverse the value graph, ignoring any values not present in any domain. Remove
            any unvisited values from every domain.
        \item Repeat whenever a value is removed from every domain during search.
    \end{itemize}
\end{frame}

@@

\begin{frame}{Connectedness in Clique-Like Algorithms}
    \begin{itemize}
        \item Connectedness doesn't decompose cleanly into binary constraints, so we can't encode it
            as microstructure.
        \item On the other hand, we \emph{can} use restricted branching, if we give more information
            to the clique algorithm.
            \begin{itemize}
                \item Integrating this with the bound and ordering heuristic used in modern clique
                    algorithms is horribly technical and was far harder than we make it look in the
                    paper (honest!).
            \end{itemize}
    \end{itemize}
\end{frame}
